\NeedsTeXFormat{LaTeX2e}
\documentclass[10pt,a4paper,twoside]{scrartcl}

\input{RGEDocPreamble}

\begin{document}
\font\TitleFont=cmbx10 at 40pt \font\SubTitleFont=cmbx10 at 25pt
\pagenumbering{arabic} \title{\TitleFont{REAP 1.11.5
}\\[1cm]\SubTitleFont{Users guide} } \author{S.~Antusch, J.~Kersten,
M.~Lindner, M.~Ratz and M.A.~Schmidt} \maketitle
\begin{abstract}
  This is an users guide of the \package{REAP} add-on
  for Mathematica. We describe the functions which allow to calculate the
  evolution of the neutrino mass matrix in different models (SM, MSSM, 2HDM).
  There is a reference of the most important functions. Besides this function
  reference there is a description of the installation procedure, a short HowTo and a section about frequently asked questions.
\end{abstract}
\thispagestyle{empty}
\tableofcontents
\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{RGELicense}
\input{RGEIntroduction}

%\begin{center}
% \fbox{\textbf{Note}: The documentation for the mixing parameter tools is in a
% separate directory!}
%\end{center}
%\input{MixingParameterTools.tex}

\input{RGEInstallation}

\input{RGEHowTo}


\section{Reference}

\subsection{Implementation details}

\package{REAP} is divided in three parts. The main part
is \package{RGESolver} which
provides a standard interface between the different models and the user. Thus
the user does not have to know anything about the implementation details of the
different models besides the parameters of the models. 
The second part are the different models, like \package{RGESM},
\package{RGEMSSM}, \dots which contain the model
specific parts of the package. 
The third part is formed by some utility packages
(\package{RGEUtilities}, \package{RGEParameters}, 
\package{RGEInitial}, \package{RGEFusaokaYukawa}, \package{RGESymbol}, \package{RGETakagi}) which provide several useful functions
to the different models. In principle, a user only needs a limited set of
functions of \package{RGESolver}.



%% The package \package{REAP} is divided in three parts. The main part is the Mathematica File \package{REAP`RGESolver`} which provides a standard interface to all model. The second part are the different models, like \package{REAP`RGESM`}, \dots ,which contain the model specific parts of the package. The third part is formed by some utility packages (\package{REAP`RGEUtilities`}, \package{REAP`RGEParameters`}, \package{REAP`RGESymbol`}, \package{REAP`RGEInitial`}, \package{REAP`RGEFusaoka`}, \package{REAP`RGETakagi`}) which provide several useful functions to the different models.

%% The \package{RGESolver} provides the interface between the user and the different models. Every model has to register with \function{RegisterModel}.
%% First the model name is saved in the list named Model. The other parameters are stored in similar lists.
%% The user has to tell to \package{RGESolver} how his model does look like. He adds several EFT's to his model by \function{RGEAddEFT}. These EFT's are stored in the list \variable{RGEModel}.


\subsubsection{RGEAdd}

\function{RGEAdd[\param{model},\optparam{options}]} 
specifies that \param{model} should be used as an effective theory (EFT)
up to a cutoff energy given in the \optparam{options}.  If no cutoff is
given, $\infty$ is used.  \optparam{options} can also be used to specify
various parameters such as $\tan\beta$.  See Sec.~\ref{sec:Models} for a
complete list of the models and options available.

\begin{verbatim}
  RGEAdd["MSSM",RGEtan\[Beta]->50]
  RGEAdd["SM",RGECutoff->10^3]
\end{verbatim}
In this case, the MSSM with $\tan\beta=50$ is used at high energies.
Below $10^3\GeV$ (the SUSY breaking scale in this example), the SM is
used as an EFT.



\subsubsection{RGEGetOptions}

\function{RGEGetOptions[\param{model}]} returns the options set by
\function{RGEAdd} or \function{RGESetOptions} for the EFT \param{model}.
Wildcards can be used in \param{model}.
 
  \begin{verbatim}
   RGEGetOptions["SM*"]
 \end{verbatim}
 This returns the options which are currently set for all EFTs whose
 names start with ``SM''.
 

\subsubsection{RGEGetParameters}

\function{RGEGetParameters[\param{model}]} returns the quantities that run
in the \param{model}.
% 
%  \begin{verbatim}
%   RGEGetParameters["SM"];
% \end{verbatim}
% This returns the parameters of the ``SM''.
% 

\subsubsection{RGEGetSolution}

\label{sec:RGEGetSolution}
\function{RGEGetSolution[\param{scale},\optparam{parameter}]} 
returns the solution of the RGEs at the energy \param{scale}.
The \optparam{parameter} (optional) specifies the quantity
of interest (cf.\ Sec.~\ref{sec:Models} for the lists for each model).
If no \optparam{parameter} is given, the values of all running
quantities are returned.


\begin{verbatim}
  RGEGetSolution[100,RGEM\[Nu]]
\end{verbatim}
returns the neutrino mass matrix at $100\GeV$.
\begin{verbatim}
  RGEGetSolution[100]
\end{verbatim}
returns all parameters at $100\GeV$.



\subsubsection{RGEGetTransitions}

\function{RGEGetTransitions[]} returns the transitions (thresholds)
between the various EFTs in a list
containing the energy scale, the model name and its options.
%
%\begin{verbatim}
%  Print[RGEGetTransitions[]];
%  {{10000000,MSSM,{}},{10000,MSSM,{RGEIntegratedOut->1}}}
%\end{verbatim}
%


\subsubsection{RGEReset}

\function{RGEReset[]} removes all EFTs and resets all options which have
been changed by \function{RGEAdd} or \function{RGESetOptions}
%functions named RGE*EFT* 
to their default values. 

\subsubsection{RGESetInitial}

\function{RGESetInitial[\param{scale},\param{initial conditions}]} sets
the initial values at the energy \param{scale}.  They are entered as
replacement rules and can also contain options (e.g.\ to select the
neutrino mass hierarchy).  See Sec.~\ref{sec:Models} for the names of
the variables and options in the different models.

\begin{verbatim}
  RGESetInitial[10^16,RGE\[Theta]13->4 Degree,RGEMlightest->0.1]
\end{verbatim}
This sets the initial values at $10^{16}\GeV$.  The mixing angle
$\theta_{13}$ is set to $4^\circ$, and the mass of the lightest neutrino
to $0.1\eV$.  For the other parameters, the default values are used.



\subsubsection{RGESetOptions}

\function{RGESetOptions[\param{model},\param{options}]} changes the options
of the EFTs defined by \function{RGEAdd} with name matching \param{model} to \param{options}. Metacharacters, like * and @, are
allowed in the name.

\begin{verbatim}
  RGESetOptions["MSSM",RGEtan\[Beta]->40]
\end{verbatim}
This sets $\tan\beta$ of the ``MSSM'' to 40.  The EFT must have been
added earlier by \function{RGEAdd["MSSM"]}.  The other options are
unchanged.



\subsubsection{RGESolve}

\function{RGESolve[\param{low},\param{high},\optparam{options}]} solves
the RGEs between the energies \param{low} and \param{high}. 

\begin{verbatim}
  RGESolve[100,10^15]
\end{verbatim}
This solves the RGEs between $100\GeV$ and $10^{15}\GeV$.
%using the method \variable{StiffnessSwitching} for the calculation.









  











%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% models
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Models\label{sec:Models}}

%\subsection{\package{RGEToyModel}}
%This package contains a toy model for testing purposes.

\subsection{Standard Model (SM)}

\subsubsection[\package{RGESM}]{\package{REAP`RGESM`}}
This package contains the Standard Model extended by an arbitrary number of right-handed neutrinos (SM)
to 1 loop order.  It is possible to automatically find transitions where heavy
neutrinos are integrated out.  However, quarks are not integrated out.

\vspace{2ex}

Options used by \function{RGESetInitial}:

If the default values of all parameters are used, the resulting parameters will
be compatible to the experimental data at the Z boson mass. The number of right-handed neutrinos is given by the initial conditions. There
is no need to specify the number of neutrinos somewhere else.
\begin{itemize}
\item RGEM$\nu$r\ is the mass matrix of the right-handed neutrinos.
  If this parameter is specified, it also determines the light neutrino
  mass matrix via the see-saw formula (together with RGEY$\nu$).  Thus,
  RGEMassHierarchy, RGEMlightest, RGE$\Delta$m2atm, RGE$\Delta$m2sol,
  RGE$\varphi$1, RGE$\varphi$2, RGE$\delta$, RGE$\delta$e,
  RGE$\delta\mu$, RGE$\delta\tau$, RGE$\theta$12, RGE$\theta$13, and
  RGE$\theta$23 do not have any effect in this case.
  
\item RGEMassHierarchy\ is the hierarchy of the neutrino masses; "r" or "n"
  means normal hierarchy, "i" means inverted hierarchy (default: "r").
  
\item RGEMlightest \ is the mass of the lightest neutrino in eV (default: $\mathcal{O}(0.01)
  \eV$).
  
\item RGEY$\nu$\ is the neutrino Yukawa matrix in ``RL convention''. This option overrides the
  built-in Yukawa matrix, i.e.\ RGEY$\nu33$ and RGEY$\nu$Ratio do not have any
  effect. 
  
\item RGEY$\nu$33\ is the (3,3) entry in the neutrino Yukawa matrix at the GUT
  scale.
\item RGEY$\nu$Ratio\ determines the relative value of the neutrino Yukawa couplings.
\item RGEYd\ is the Yukawa matrix of the down-type quarks.
  If this parameter is given, RGEyd, RGEys, RGEyb, RGEq$\varphi$1,
  RGEq$\varphi$2, RGEq$\delta$, RGEq$\delta$e, RGEq$\delta\mu$,
  RGEq$\delta\tau$, RGEq$\theta$12, RGEq$\theta$13, and RGEq$\theta$23
  are ignored.
  
\item RGEYe\ is the charged lepton Yukawa matrix.
  If this parameter is given, RGEye, RGEy$\mu$ and RGEy$\tau$ are
  ignored.
  
\item RGEYu\ is the Yukawa matrix of the up-type quarks.
  If this parameter is given, RGEyu, RGEyc and RGEyt are ignored;
  it is recommended not to use RGEq$\varphi$1, RGEq$\varphi$2,
  RGEq$\delta$, RGEq$\delta$e, RGEq$\delta\mu$, RGEq$\delta\tau$,
  RGEq$\theta$12, RGEq$\theta$13, and RGEq$\theta$23 in this case, since
  they are not necessarily equal to the CKM mixing parameters.
\item RGE$\Delta$m2atm\ is the atmospheric mass squared difference (default: $ \mathcal{O}(10^{-3}) \eV^2$).
\item RGE$\Delta$m2sol\ is the solar mass squared difference (default:
  $\mathcal{O}(10^{-4}) \eV^2$).
\item RGE$\varphi$1\ and RGE$\varphi2$ are the Majorana CP phases $\varphi_1$ and $\varphi_2$ in radians (default: $0$).
  
\item RGE$\delta$\ is the Dirac CP phase $\delta$ in radians (default: $0$).
\item RGE$\delta$e, RGE$\delta\mu$ and RGE$\delta\tau$ are the unphysical phases $\delta_e$,
  $\delta_\mu$ and $\delta_\tau$ (default: $0$). 
\item RGE$\kappa$\ is the coupling of the dimension 5 neutrino mass operator.
  
\item RGE$\lambda$\ is the quartic Higgs self-coupling (default: 0.5).  We use the
  convention that the corresponding term in the Lagrangian is
  $-\frac{\lambda}{4} (\phi^\dagger \phi)^2$.
  
\item RGE$\theta$12, RGE$\theta13$ and RGE$\theta23$ are the angles $\theta_{12}$, $\theta_{13}$
and $\theta_{23}$ of the MNS matrix in radians. (default: $\theta_{13}=0$ and
$\theta_{23}=\frac{\pi}{4}$). The default of $\theta_{12}$ depends on the
model. It is chosen in such a way, that the parameters are compatible with the
experimental data. 
\item RGEg RGEg is the coupling constants of SU(5)
  
\item RGEg1, RGEg2 and RGEg3 are the coupling constants of U$(1)_\mathrm{Y}$,
  SU$(2)_\mathrm{L}$ and SU$(3)_\mathrm{C}$, respectively.  GUT charge
  normalization is used for $g_1$.
  
\item RGEm RGEm is the Higgs mass
  
\item RGEq$\varphi$1\ and RGEq$\varphi2$ are the unphysical phases $\varphi_1$ and $\varphi_2$ of the
 CKM matrix which correspond to the Majorana phases in the MNS matrix (default: $0$).
\item RGEq$\delta$\ is the Dirac CP phase $\delta$ of the CKM matrix.
\item RGEq$\delta$e, RGEq$\delta\mu$ and RGE$\delta\tau$ are the unphysical phases $\delta_e$,
$\delta_\mu$ and $\delta_\tau$ of the CKM matrix (default: $0$).
\item RGEq$\theta$12, RGEq$\theta13$ and RGEq$\theta23$ are the angles of the CKM matrix. 
\item RGEyd, RGEys and RGEyb are the Yukawa coupling of the down-type quarks $d$,
  $s$ and $b$.
\item RGEye, RGEy$\mu$ and RGEy$\tau$ are the Yukawa couplings of the charged
  leptons $e$, $\mu$ and $\tau$.
\item RGEyu, RGEyc and RGEyt are the Yukawa couplings of the up-type quarks $u$,
  $c$ and $t$.

\end{itemize}

Parameters accepted by \function{RGEGetSolution}:
\begin{itemize}
\item 
RGECoupling is used to get the coupling constants.
\item 
RGEGWCondition returns the Gildener Weinberg condition.
\item 
RGEGWConditions returns all Gildener Weinberg conditions.
\item 
RGEM$\nu$ is used to get the mass matrix of the left-handed neutrinos.
\item 
RGEM$\nu$r is the mass matrix of the right-handed neutrinos.
\item 
RGEMd is used to get the mass matrix of the down-type quarks.
\item 
RGEMe is used to get the mass matrix of the charged leptons.
\item 
RGEMu is used to get the mass matrix of the up-type quarks.
\item 
RGERawY$\Delta$ is used to get the Yukawa coupling matrix of the coupling to the Higgs triplet.
\item 
RGEAll returns all parameters of the model.
\item 
RGEVEVratio returns the squared ratio of $v_R$ over the EW symmetry breaking scale.
\item 
RGEVEVratios returns the squared ratio of $v_R$ over the EW symmetry breaking scale.
\item 
RGEY$\nu$ is used to get the Yukawa coupling matrix of the neutrinos.
\item 
RGEYd is used to get the Yukawa coupling matrix of the down-type quarks.
\item 
 RGEYe is used to get the Yukawa coupling matrix of the charged leptons.
\item 
RGEYu is used to get the Yukawa coupling matrix of the up-type quarks.
\item 
RGE$\alpha$ is used to get the fine structure constants.
\item 
RGE$\lambda$ is used to get the quartic Higgs self coupling.

\end{itemize}

\subsubsection[\package{RGESM0N}]{\package{REAP`RGESM0N`}}
This package contains the Standard Model without any right-handed neutrinos
(SM0N) to 1 loop order.

\vspace{2ex} It has the same parameters and options as \package{RGESM},
with the following exceptions:  The only
missing options are RGEIntegratedOut, RGESearchTransition, RGEThresholdFactor,
RGEPrecision and RGEMaxNumberIterations, which are used to control the process
of integrating out.  Besides, RGEM$\nu$r and RGEY$\nu$ are no parameters of
\function{RGESetInitial}, and RGE$\epsilon$Max, RGE$\epsilon$, RGEM1Tilde, RGERawM$\nu$r and RGERawY$\nu$ are not accepted as
parameters by \function{RGEGetSolution}.  \function{RGESetInitial} has
an additional option: RGESuggestion can be used to choose between
different sets of default values, ``GUT'' (default) and ``MZ''.  They
refer to typical parameter values at the GUT scale or at the $Z$ mass,
respectively.

\subsubsection[\package{RGESMDirac}]{\package{REAP`RGESMDirac`}}
This package contains the Standard Model with Dirac Neutrinos to 1 loop order.

\vspace{2ex} It has the same parameters and options as \package{RGESM},
with the following exceptions:  The only
missing options are RGEIntegratedOut, RGESearchTransition, RGEThresholdFactor,
RGEPrecision and RGEMaxNumberIterations, which are used to control the process
of integrating out.  In addition RGE$\kappa$ and RGEM$\nu$r are no parameters of
\function{RGESetInitial} and RGEMixingParameters, RGE$\epsilon$Max, RGE$\epsilon$, RGEM1Tilde, RGERawM$\nu$r, RGERawY$\nu$ and RGE$\kappa$ are not
accepted as parameters by \function{RGEGetSolution}.
\function{RGESetInitial} has an additional option: RGESuggestion can be
used to choose between different sets of default values, ``GUT''
(default) and ``MZ''.  They refer to typical parameter values at the GUT
scale or at the $Z$ mass, respectively.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Minimal Supersymmetric Standard Model (MSSM)}

\subsubsection[\package{RGEMSSM}]{\package{REAP`RGEMSSM`}}
This package contains the Minimal Supersymmetric Standard Model extended by an arbitrary number of 
right-handed neutrinos (MSSM) to 1 and 2 loop order.

It is possible to automatically find transitions where heavy neutrinos are
integrated out.  But neither quarks are integrated out nor MSSM thresholds are
considered. 

Options:
\begin{itemize}
\item RGE$\Gamma$d\ parameterizes the finite supersymmetric threshold corrections
\begin{equation}
Y_d^\mathrm{SM} = Y_d^\mathrm{MSSM} (1 + \mathrm{RGE}\Gamma\mathrm{d}) * \cos(\beta)
\end{equation}
in the basis, in which $Y_u$ is diagonal and the left-handed mixing is entirely contained in $Y_d$. It is related to the notation in \cite{Blazek:1995nv}
\begin{equation}
\mathrm{RGE}\Gamma\mathrm{d} \equiv \epsilon (V_{CKM} \Gamma_D^\dagger V_{CKM}^\dagger +\Gamma_U^\dagger)
\end{equation}
with $\epsilon = \tan\beta/(16 \pi^2)$ and $\Gamma_{U,D}$ defines as in Eq.~(1) of Ref.~\cite{Blazek:1995nv}. 
\item RGE$\Gamma$e\ parameterizes the finite supersymmetric threshold corrections
\begin{equation}
Y_e^\mathrm{SM} = Y_e^\mathrm{MSSM} (1 + \mathrm{RGE}\Gamma\mathrm{e}) * \cos\beta
\end{equation}
in the basis, in which the Weinberg operator $\kappa$ is diagonal and the left-handed mixing is entirely contained in $Y_e$. It is defined in a similar way to RGE$\Gamma$d.
\item RGEtan$\beta$\ is the value of $\tan\beta=\frac{v_u}{v_d}$, the ratio of the 2
  Higgs vevs (default: 50).

\end{itemize}

Options used by \function{RGESetInitial}:

If the default values of all parameters are used, the resulting parameters will
be compatible to the experimental data at the Z boson mass. The number of right-handed neutrinos is given by the initial conditions. There
is no need to specify the number of neutrinos somewhere else.
\begin{itemize}
\item RGEM$\nu$r\ is the mass matrix of the right-handed neutrinos.
  If this parameter is specified, it also determines the light neutrino
  mass matrix via the see-saw formula (together with RGEY$\nu$).  Thus,
  RGEMassHierarchy, RGEMlightest, RGE$\Delta$m2atm, RGE$\Delta$m2sol,
  RGE$\varphi$1, RGE$\varphi$2, RGE$\delta$, RGE$\delta$e,
  RGE$\delta\mu$, RGE$\delta\tau$, RGE$\theta$12, RGE$\theta$13, and
  RGE$\theta$23 do not have any effect in this case.
  
\item RGEMassHierarchy\ is the hierarchy of the neutrino masses; "r" or "n"
  means normal hierarchy, "i" means inverted hierarchy (default: "r").
  
\item RGEMlightest \ is the mass of the lightest neutrino in eV (default: $\mathcal{O}(0.01)
  \eV$).
  
\item RGEY$\nu$\ is the neutrino Yukawa matrix in ``RL convention''. This option overrides the
  built-in Yukawa matrix, i.e.\ RGEY$\nu33$ and RGEY$\nu$Ratio do not have any
  effect. 
  
\item RGEY$\nu$33\ is the (3,3) entry in the neutrino Yukawa matrix at the GUT
  scale.
\item RGEY$\nu$Ratio\ determines the relative value of the neutrino Yukawa couplings.
\item RGEYd\ is the Yukawa matrix of the down-type quarks.
  If this parameter is given, RGEyd, RGEys, RGEyb, RGEq$\varphi$1,
  RGEq$\varphi$2, RGEq$\delta$, RGEq$\delta$e, RGEq$\delta\mu$,
  RGEq$\delta\tau$, RGEq$\theta$12, RGEq$\theta$13, and RGEq$\theta$23
  are ignored.
  
\item RGEYe\ is the charged lepton Yukawa matrix.
  If this parameter is given, RGEye, RGEy$\mu$ and RGEy$\tau$ are
  ignored.
  
\item RGEYu\ is the Yukawa matrix of the up-type quarks.
  If this parameter is given, RGEyu, RGEyc and RGEyt are ignored;
  it is recommended not to use RGEq$\varphi$1, RGEq$\varphi$2,
  RGEq$\delta$, RGEq$\delta$e, RGEq$\delta\mu$, RGEq$\delta\tau$,
  RGEq$\theta$12, RGEq$\theta$13, and RGEq$\theta$23 in this case, since
  they are not necessarily equal to the CKM mixing parameters.
\item RGE$\Delta$m2atm\ is the atmospheric mass squared difference (default: $ \mathcal{O}(10^{-3}) \eV^2$).
\item RGE$\Delta$m2sol\ is the solar mass squared difference (default:
  $\mathcal{O}(10^{-4}) \eV^2$).
\item RGE$\varphi$1\ and RGE$\varphi2$ are the Majorana CP phases $\varphi_1$ and $\varphi_2$ in radians (default: $0$).
  
\item RGE$\delta$\ is the Dirac CP phase $\delta$ in radians (default: $0$).
\item RGE$\delta$e, RGE$\delta\mu$ and RGE$\delta\tau$ are the unphysical phases $\delta_e$,
  $\delta_\mu$ and $\delta_\tau$ (default: $0$). 
\item RGE$\kappa$\ is the coupling of the dimension 5 neutrino mass operator.
  
\item RGE$\theta$12, RGE$\theta13$ and RGE$\theta23$ are the angles $\theta_{12}$, $\theta_{13}$
and $\theta_{23}$ of the MNS matrix in radians. (default: $\theta_{13}=0$ and
$\theta_{23}=\frac{\pi}{4}$). The default of $\theta_{12}$ depends on the
model. It is chosen in such a way, that the parameters are compatible with the
experimental data. 
\item RGEg RGEg is the coupling constants of SU(5)
  
\item RGEg1, RGEg2 and RGEg3 are the coupling constants of U$(1)_\mathrm{Y}$,
  SU$(2)_\mathrm{L}$ and SU$(3)_\mathrm{C}$, respectively.  GUT charge
  normalization is used for $g_1$.
  
\item RGEm RGEm is the Higgs mass
  
\item RGEq$\varphi$1\ and RGEq$\varphi2$ are the unphysical phases $\varphi_1$ and $\varphi_2$ of the
 CKM matrix which correspond to the Majorana phases in the MNS matrix (default: $0$).
\item RGEq$\delta$\ is the Dirac CP phase $\delta$ of the CKM matrix.
\item RGEq$\delta$e, RGEq$\delta\mu$ and RGE$\delta\tau$ are the unphysical phases $\delta_e$,
$\delta_\mu$ and $\delta_\tau$ of the CKM matrix (default: $0$).
\item RGEq$\theta$12, RGEq$\theta13$ and RGEq$\theta23$ are the angles of the CKM matrix. 
\item RGEyd, RGEys and RGEyb are the Yukawa coupling of the down-type quarks $d$,
  $s$ and $b$.
\item RGEye, RGEy$\mu$ and RGEy$\tau$ are the Yukawa couplings of the charged
  leptons $e$, $\mu$ and $\tau$.
\item RGEyu, RGEyc and RGEyt are the Yukawa couplings of the up-type quarks $u$,
  $c$ and $t$.

\end{itemize}

Parameters accepted by \function{RGEGetSolution}:
\begin{itemize}
\item 
RGECoupling is used to get the coupling constants.
\item 
RGEGWCondition returns the Gildener Weinberg condition.
\item 
RGEGWConditions returns all Gildener Weinberg conditions.
\item 
RGEM$\nu$ is used to get the mass matrix of the left-handed neutrinos.
\item 
RGEM$\nu$r is the mass matrix of the right-handed neutrinos.
\item 
RGEMd is used to get the mass matrix of the down-type quarks.
\item 
RGEMe is used to get the mass matrix of the charged leptons.
\item 
RGEMu is used to get the mass matrix of the up-type quarks.
\item 
RGERawY$\Delta$ is used to get the Yukawa coupling matrix of the coupling to the Higgs triplet.
\item 
RGEAll returns all parameters of the model.
\item 
RGEVEVratio returns the squared ratio of $v_R$ over the EW symmetry breaking scale.
\item 
RGEVEVratios returns the squared ratio of $v_R$ over the EW symmetry breaking scale.
\item 
RGEY$\nu$ is used to get the Yukawa coupling matrix of the neutrinos.
\item 
RGEYd is used to get the Yukawa coupling matrix of the down-type quarks.
\item 
 RGEYe is used to get the Yukawa coupling matrix of the charged leptons.
\item 
RGEYu is used to get the Yukawa coupling matrix of the up-type quarks.
\item 
RGE$\alpha$ is used to get the fine structure constants.
\item 
RGE$\kappa$ is used to get $\kappa$.

\end{itemize}

\subsubsection[\package{RGEMSSM0N}]{\package{REAP`RGEMSSM0N`}}
This package contains the Minimal Supersymmetric Standard Model (MSSM) without
any right-handed neutrinos to 1 and 2 loop order.

\vspace{2ex} It has the same parameter and options as \package{RGEMSSM}.  The
only missing options are RGEIntegratedOut, RGESearchTransition,
RGEThresholdFactor, RGEPrecision and RGEMaxNumberIterations, which are used to
control the process of integrating out.  In addition RGEM$\nu$r and RGEY$\nu$
are no parameters of \function{RGESetInitial} and RGE$\epsilon$Max,
RGE$\epsilon$, RGEM1Tilde, RGERawM$\nu$r and RGERawY$\nu$
are not accepted as parameters by \function{RGEGetSolution}.


\subsubsection[\package{RGEMSSMDirac}]{\package{REAP`RGEMSSMDirac`}}
This package contains the MSSM with Dirac Neutrinos to 1 loop order and 2 loop
order.

\vspace{2ex} It has the same parameter and options as \package{RGEMSSM}.  The
only missing options are RGEIntegratedOut, RGESearchTransition,
RGEThresholdFactor, RGEPrecision and RGEMaxNumberIterations, which are used to
control the process of integrating out.  In addition RGEM$\nu$r and RGE$\kappa$
are no parameter of \function{RGESetInitial} and RGEMixingParameters, RGE$\epsilon$Max,
RGE$\epsilon$, RGEM1Tilde, RGERawM$\nu$r, RGERawY$\nu$ and
RGE$\kappa$ are not accepted as parameters by \function{RGEGetSolution}.

\subsection{Two Higgs Doublet Model (2HDM)}

\subsubsection[\package{RGE2HDM}]{\package{REAP`RGE2HDM`}}
This package contains the Two Higgs Doublet Model (2HDM) with a $\mathbb{Z}_2$
symmetry extended by an arbitrary number of right-handed neutrinos. The charged leptons always couple to the first Higgs. In addition
there are right-handed neutrinos. The $\beta$-functions are to 1 loop order. The
vevs of the Higgs fields are $v_1=\braket{\phi_1}$ and
$v_2=\braket{\phi_2}$. They obey $v^2=v_1^2+v_2^2$, $v_1=v\cos\beta$ and
$v_2=v\sin\beta$, where v is the v.e.v. of the SM Higgs and $\beta$
($\tan\beta=\frac{v_2}{v_1}$, $\beta\in\left(0,\frac{\pi}{2}\right)$) is used to
parametrize the Higgs vevs.

Thus there are 2 dimension 5 operators which give mass to the light neutrinos.
\begin{equation*}
  \mathcal{L}_\kappa^{(ii)}=\frac{1}{4}\kappa_{gf}^{(ii)}\overline{l_{Lc}^C}^g\epsilon^{cd}\phi_d^{(i)}l_{Lb}^f\epsilon^{ba}\phi_a^{(i)}+\mathrm{h.c.}\quad\quad(i=1\;
  or\; 2)
\end{equation*}
The Higgs potential is
\begin{eqnarray*}
\mathcal{L}_{2Higgs}&=& -\frac{\lambda_1}{4}
\left(\phi^{(1)\dagger}\phi^{(1)}\right)^2 -\frac{\lambda_2}{4}
\left(\phi^{(2)\dagger}\phi^{(2)}\right)^2\\
&&-\lambda_3\left(\phi^{(1)\dagger}\phi^{(1)}\right)\left(\phi^{(2)\dagger}\phi^{(2)}\right)
-\lambda_4\left(\phi^{(1)\dagger}\phi^{(2)}\right)\left(\phi^{(2)\dagger}\phi^{(1)}\right)
\\ &&
-\left[\frac{\lambda_5}{4}\left(\phi^{(1)\dagger}\phi^{(2)}\right)^2+\mathrm{h.c.}\right]\\
\end{eqnarray*}

The charged leptons always couple to the first Higgs field and the coupling of
the other fields to the Higgs fields is determined by RGEModelOptions.

It is possible to automatically find transitions where heavy neutrinos are
integrated out.  But no other particles are integrated out.

Options:
\begin{itemize}
\item RGEtan$\beta$ is the value of $\tan\beta=\frac{v_2}{v_1}$, the ratio of the 2
  Higgs vevs (default: 50).
\item RGEz$\nu$\ is a list defining the Higgs the neutrinos are coupling to. If the $n^{th}$ component is one,
    the Higgs couples to the neutrinos. If it is 0, it won't
    couple (default: $\{0,1\}$). The charged leptons always couple to the
  first Higgs.
\item RGEzd\ is a list defining the Higgs the down-type quarks are coupling to. If the $n^{th}$ component is one,
    the Higgs couples to the down-type quarks. If it is 0, it won't
    couple (default: $\{1,0\}$).
\item RGEzu\ is a list defining the Higgs the up-type quarks are coupling to. If the $n^{th}$ component is one,
    the Higgs couples to the up-type quarks. If it is 0, it won't
    couple (default: $\{0,1\}$).

\end{itemize}

Options used by \function{RGESetInitial}:

If the default values of all parameters are used, the resulting parameters will
be compatible to the experimental data at the Z boson mass. The number of right-handed neutrinos is given by the initial conditions. There
is no need to specify the number of neutrinos somewhere else.
\begin{itemize}
\item RGEM$\nu$r\ is the mass matrix of the right-handed neutrinos.
  If this parameter is specified, it also determines the light neutrino
  mass matrix via the see-saw formula (together with RGEY$\nu$).  Thus,
  RGEMassHierarchy, RGEMlightest, RGE$\Delta$m2atm, RGE$\Delta$m2sol,
  RGE$\varphi$1, RGE$\varphi$2, RGE$\delta$, RGE$\delta$e,
  RGE$\delta\mu$, RGE$\delta\tau$, RGE$\theta$12, RGE$\theta$13, and
  RGE$\theta$23 do not have any effect in this case.
  
\item RGEMassHierarchy\ is the hierarchy of the neutrino masses; "r" or "n"
  means normal hierarchy, "i" means inverted hierarchy (default: "r").
  
\item RGEMlightest \ is the mass of the lightest neutrino in eV (default: $\mathcal{O}(0.01)
  \eV$).
  
\item RGEY$\nu$\ is the neutrino Yukawa matrix in ``RL convention''. This option overrides the
  built-in Yukawa matrix, i.e.\ RGEY$\nu33$ and RGEY$\nu$Ratio do not have any
  effect. 
  
\item RGEY$\nu$33\ is the (3,3) entry in the neutrino Yukawa matrix at the GUT
  scale.
\item RGEY$\nu$Ratio\ determines the relative value of the neutrino Yukawa couplings.
\item RGEYd\ is the Yukawa matrix of the down-type quarks.
  If this parameter is given, RGEyd, RGEys, RGEyb, RGEq$\varphi$1,
  RGEq$\varphi$2, RGEq$\delta$, RGEq$\delta$e, RGEq$\delta\mu$,
  RGEq$\delta\tau$, RGEq$\theta$12, RGEq$\theta$13, and RGEq$\theta$23
  are ignored.
  
\item RGEYe\ is the charged lepton Yukawa matrix.
  If this parameter is given, RGEye, RGEy$\mu$ and RGEy$\tau$ are
  ignored.
  
\item RGEYu\ is the Yukawa matrix of the up-type quarks.
  If this parameter is given, RGEyu, RGEyc and RGEyt are ignored;
  it is recommended not to use RGEq$\varphi$1, RGEq$\varphi$2,
  RGEq$\delta$, RGEq$\delta$e, RGEq$\delta\mu$, RGEq$\delta\tau$,
  RGEq$\theta$12, RGEq$\theta$13, and RGEq$\theta$23 in this case, since
  they are not necessarily equal to the CKM mixing parameters.
\item RGE$\Delta$m2atm\ is the atmospheric mass squared difference (default: $ \mathcal{O}(10^{-3}) \eV^2$).
\item RGE$\Delta$m2sol\ is the solar mass squared difference (default:
  $\mathcal{O}(10^{-4}) \eV^2$).
\item RGE$\varphi$1\ and RGE$\varphi2$ are the Majorana CP phases $\varphi_1$ and $\varphi_2$ in radians (default: $0$).
  
\item RGE$\delta$\ is the Dirac CP phase $\delta$ in radians (default: $0$).
\item RGE$\delta$e, RGE$\delta\mu$ and RGE$\delta\tau$ are the unphysical phases $\delta_e$,
  $\delta_\mu$ and $\delta_\tau$ (default: $0$). 
\item RGE$\kappa$1\ is the coupling of the dimension 5 operator associated
  with the first Higgs in the 2HDM.
  
\item RGE$\kappa$2\ is the coupling of the dimension 5 operator associated
  with the second Higgs in the 2HDM.
  
\item RGE$\lambda$1, RGE$\lambda2$, RGE$\lambda3$, RGE$\lambda4$ and RGE$\lambda5$ are the parameters
$\lambda_1$, $\lambda_2$, $\lambda_3$, $\lambda_4$ and $\lambda_5$ in the Higgs potential
(default: $\lambda_1=\lambda_2=0.75$, $\lambda_3=\lambda_4=0.2$, $\lambda_5=0.25$).
\item RGE$\theta$12, RGE$\theta13$ and RGE$\theta23$ are the angles $\theta_{12}$, $\theta_{13}$
and $\theta_{23}$ of the MNS matrix in radians. (default: $\theta_{13}=0$ and
$\theta_{23}=\frac{\pi}{4}$). The default of $\theta_{12}$ depends on the
model. It is chosen in such a way, that the parameters are compatible with the
experimental data. 
\item RGEg RGEg is the coupling constants of SU(5)
  
\item RGEg1, RGEg2 and RGEg3 are the coupling constants of U$(1)_\mathrm{Y}$,
  SU$(2)_\mathrm{L}$ and SU$(3)_\mathrm{C}$, respectively.  GUT charge
  normalization is used for $g_1$.
  
\item RGEm RGEm is the Higgs mass
  
\item RGEq$\varphi$1\ and RGEq$\varphi2$ are the unphysical phases $\varphi_1$ and $\varphi_2$ of the
 CKM matrix which correspond to the Majorana phases in the MNS matrix (default: $0$).
\item RGEq$\delta$\ is the Dirac CP phase $\delta$ of the CKM matrix.
\item RGEq$\delta$e, RGEq$\delta\mu$ and RGE$\delta\tau$ are the unphysical phases $\delta_e$,
$\delta_\mu$ and $\delta_\tau$ of the CKM matrix (default: $0$).
\item RGEq$\theta$12, RGEq$\theta13$ and RGEq$\theta23$ are the angles of the CKM matrix. 
\item RGEyd, RGEys and RGEyb are the Yukawa coupling of the down-type quarks $d$,
  $s$ and $b$.
\item RGEye, RGEy$\mu$ and RGEy$\tau$ are the Yukawa couplings of the charged
  leptons $e$, $\mu$ and $\tau$.
\item RGEyu, RGEyc and RGEyt are the Yukawa couplings of the up-type quarks $u$,
  $c$ and $t$.

\end{itemize}

Parameters accepted by \function{RGEGetSolution}:
\begin{itemize}
\item 
RGECoupling is used to get the coupling constants.
\item 
RGEGWCondition returns the Gildener Weinberg condition.
\item 
RGEGWConditions returns all Gildener Weinberg conditions.
\item 
RGEM$\nu$ is used to get the mass matrix of the left-handed neutrinos.
\item 
RGEM$\nu$r is the mass matrix of the right-handed neutrinos.
\item 
RGEMd is used to get the mass matrix of the down-type quarks.
\item 
RGEMe is used to get the mass matrix of the charged leptons.
\item 
RGEMu is used to get the mass matrix of the up-type quarks.
\item 
RGERawY$\Delta$ is used to get the Yukawa coupling matrix of the coupling to the Higgs triplet.
\item 
RGEAll returns all parameters of the model.
\item 
RGEVEVratio returns the squared ratio of $v_R$ over the EW symmetry breaking scale.
\item 
RGEVEVratios returns the squared ratio of $v_R$ over the EW symmetry breaking scale.
\item 
RGEY$\nu$ is used to get the Yukawa coupling matrix of the neutrinos.
\item 
RGEYd is used to get the Yukawa coupling matrix of the down-type quarks.
\item 
 RGEYe is used to get the Yukawa coupling matrix of the charged leptons.
\item 
RGEYu is used to get the Yukawa coupling matrix of the up-type quarks.
\item 
RGE$\alpha$ is used to get the fine structure constants.
\item 
RGE$\kappa$1 is the parameter of the dimension 5 operator associated
  with the first Higgs in the 2HDM.
\item 
RGE$\kappa$2 is the parameter of the dimension 5 operator associated
  with the second Higgs in the 2HDM.
  
\item 
RGE$\lambda$ is used to get the Higgs couplings.

\end{itemize}

  

\subsubsection[\package{RGE2HDM0N}]{\package{REAP`RGE2HDM0N`}}
This package contains the Two Higgs Doublet Model (2HDM) with a $\mathbb{Z}_2$
symmetry without right-handed neutrinos.

\vspace{2ex} It has the same parameters and options as
\package{RGE2HDM}, with the following exceptions:  The
only missing options are RGEIntegratedOut, RGESearchTransition,
RGEThresholdFactor, RGEPrecision and RGEMaxNumberIterations, which are used to
control the process of integrating out.  In addition RGEM$\nu$r and RGEY$\nu$
are no parameters of \function{RGESetInitial} and RGEM1Tilde, RGERawM$\nu$r and RGERawY$\nu$
are not accepted as parameters by \function{RGEGetSolution}.
\function{RGESetInitial} has an additional option: RGESuggestion can be
used to choose between different sets of default values, ``GUT''
(default) and ``MZ''.  They refer to typical parameter values at the GUT
scale or at the $Z$ mass, respectively.


\subsubsection[\package{RGE2HDMDirac}]{\package{REAP`RGE2HDMDirac`}}
This package contains the 2HDM with Dirac neutrinos to 1 loop order.

\vspace{2ex} It has the same parameters and options as
\package{RGE2HDM}, with the following exceptions: The
only missing options are RGEIntegratedOut, RGESearchTransition,
RGEThresholdFactor, RGEPrecision and RGEMaxNumberIterations, which are used to
control the process of integrating out.  In addition RGEM$\nu$r, RGE$\kappa$1
and RGE$\kappa$2 are no parameter of \function{RGESetInitial} and
RGEMixingParameters, RGEM1Tilde, RGERawM$\nu$r,
RGERawY$\nu$, RGE$\kappa$1 and RGE$\kappa$2 are not accepted as parameters by
\function{RGEGetSolution}.
\function{RGESetInitial} has an additional option: RGESuggestion can be
used to choose between different sets of default values, ``GUT''
(default) and ``MZ''.  They refer to typical parameter values at the GUT
scale or at the $Z$ mass, respectively.


%\input{RGEShortReference}
%\input{RGEModels}

\input{RGEFAQ}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\bibliography{reap}

\end{document}

